Storing messages with multipartite neural cliques

### 2014-07-21 Articles/article.tex
...

		\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/fig3c4l512e2a2} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
			\label{erasuresth}
		\end{figure}

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 units per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\label{corruptth}
	\end{figure}

>>>>

		\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/fig3c4l512e2a2} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
			\label{erasuresth}
		\end{figure}

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/fig4c4l512a2e1corr}%remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 units per cluster, one erroneous cluster, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{corruptth}
	\end{figure}
